### 2015-10-27 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
Suggestions by Ed Zalta inserted

This work significantly adapts and extends the embedding presented in \cite{J23}; say more ...%

@@

\isamarkupcmt{modal logic formulas (or propositional formulas) are essentially of this type: predicates on%
\isamarkupcmt{worlds%

@@

\isamarkupcmt{some fixed current world%

@@

\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are on-empty%

@@

We consider an arbitrary but fixed accessibility relation r%
\ r\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharparenleft}i{\isasymRightarrow}i{\isasymRightarrow}bool{\isacharparenright}{\isachardoublequoteclose}%

@@

\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline

@@

\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline
\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline

@@

box operator; \isa{{\isasymbox}\isactrlsup r\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on%

@@

\isamarkupsection{Some shorthands for the constructors%

@@

An example signature; entities and relations%

@@

Testing some term and formula constructions%

@@

\isamarkupsection{Get the priorities right%

@@

Distinguished 1-place Relation Constant: E! (read: ‘being concrete’ or ‘concreteness’)%

@@

Question: is the term above a Form or a PropForm?%

@@

\isamarkupsection{Some further examples%

>>>>

This work is related to \cite{J23}, which is significantly extends ...%

@@

\isamarkupcmt{formulas are essentially of this type%
\isamarkupcmt{predicates on worlds%

@@

\isamarkupcmt{the distinguished actual world%

@@

\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are non-empty%

@@

@@

\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline

@@

\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline

@@

box operator; \isa{{\isasymbox}\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on.
Note that the \isa{{\isasymbox}}-operator is defined here without an accessibility relation; this is ok since we assume logic S5.%

@@

\isamarkupsection{Some shortcuts for the constructors%

@@

Example signature; entities and relations%

@@

Testing term and formula constructions%

@@

\isamarkupsection{Are the priorities set correctly?%

@@

Distinguished 1-place relation constant: E! (read: ‘being concrete’ or ‘concreteness’)%

@@

@@

\isamarkupsection{Further test examples%
